### 2015-06-16 writing/S'15 LSTM/data.tex
Abstract formatting for pasting, final tweaks.

\paragraph{The corpus}
The sentence pairs in the corpus are divided into thirteen bins according to the number of logical connectives (\word{and, or, not}) in the longer of the two sentences in the pair. We test the model on each bin separately (58k total examples, using an 80/20\% train/test split) in order to evaluate how its performance depends on the complexity of the sentences. In three experiments, we train our models on the training portions of bins 0--3 (62k examples), 0--4 (90k), and 0--6 (160k), and test on every bin but the trivial bin 0. Capping the size of the training sentences allows us to evaluate how the models interpret the sentences: if their performance falls off abruptly above the cutoff, it is reasonable to assume that the models are depending heavily on specific sentence structures, and cannot generalize to new structures. If their performance decays gradually\footnote{Since sentences are fixed-dimensional vectors of fixed-precision floating point numbers, all models will make errors on sentences above some length, and L2 regularization (which helps overall performance) exacerbates this by preventing the model from using the kind of numerically precise, nonlinearity-saturating functions that would generalize best.} with no such abrupt change, then it must have learned a more generally valid interpretation function for the language which respects its recursive structure.

>>>>

\paragraph{The corpus}
The sentence pairs in the corpus are divided into thirteen bins according to the number of logical connectives (\word{and, or, not}) in the longer of the two sentences in the pair. We test the model on each bin separately (58k total examples, using an 80/20\% train/test split) in order to evaluate how its performance depends on the complexity of the sentences. In three experiments, we train our models on the training portions of bins 0--3 (62k examples), 0--4 (90k), and 0--6 (160k), and test on every bin but the trivial bin 0. Capping the size of the training sentences allows us to evaluate how the models interpret the sentences: if their performance falls off abruptly above the cutoff, it is reasonable to assume that the models are depending heavily on specific sentence structures, and cannot generalize to new structures. If their performance decays gradually\footnote{Since sentences are fixed-dimensional vectors of fixed-precision floating point numbers, all models will make errors on sentences above some length, and L2 regularization (which helps overall performance) exacerbates this by discouraging the model from using the kind of numerically precise, nonlinearity-saturating functions that would generalize best.} with no such abrupt change, then it must have learned a more generally valid interpretation function for the language which respects its recursive structure.
